\afterpage{%
\newgeometry{
top=1.25in,
bottom=1.25in,
left=1.25in,
right=1.25in,
bindingoffset=0.25in,
heightrounded
}
\addcontentsline{toc}{chapter}{Acknowledgments}
\thispagestyle{empty}

\vspace*{20mm}

\begin{center}
{\usekomafont{section} Acknowledgments}
\end{center}
\vspace{10mm}

Where do I even begin? 
I have many people to thank for their tremendous support in this thesis, but first I want to start with the one person who truly made it all possible: my supervisor, \textit{Paloma}!

Not only did you always have time for my questions and discussions, but you also showed a level of enthusiasm and passion for this problem I could not have wished more.

And yes, thank you for achieving your main mission that was to do everything to "find you a PhD programm".

Furthermore, I would like to express my sincere gratitude to my professor at TUM, \textit{Prof. Ghoshdastidar}, for agreeing to formally supervise my thesis. 
Your immediate willingness to take on this role and the uncomplicated communication was greatly appreciated!

Furthermore, I would like to thank the whole algorithms group at ITU for letting me be a part of the group despite my status as a \textit{mere} Master student.

From the moment I joined the group, you all made me feel welcome and integrated, and I am grateful for the opportunity to do my thesis in such a friendly and helpful environment 

Thank you to Riko for inviting me to this year's Retriet, the running sessios with Martin and Christian
% Nutan, Radu,

Another special thanks to Jan Arne at UiB for introducing me into the fascinating world of parameterized Complexity and engaging me to further dig into this area! 

% Atos
My employer Atos for providing me with the necessary flexibility of working hours 

Lastly, I would like to thank openAI's \textit{chatGPT Dec 15} for writing this acknowledgments section and \textit{Dall-E 2} for the immense amount of creativity that went into the chapter's illustrations!
What a time to be alive!


\cleardoublepage{}

\clearpage
\restoregeometry}