\chapter{Abstract}

\begin{abstract}
{\sffamily
For a graph \G, a set $D$ is called a \textit{semitotal dominating set}, if $D$ is a dominating set and every vertex $v \in D$ is within distance two to another witness $v' \in D$. 
The \msdom problem is to find a semitotal dominating set of minimum cardinality. 
The semitotal domination number $\gamma_{t2}(G)$ is the minimum cardinality of a semitotal dominating set and is squeezed between the domination number $\gamma(G)$ and the total domination number $\gamma_t(G)$.
 Given \G and a positive integer $k$, the \sdomd problem asks if $\gamma_{2t} \leq k$.

After introduced by Goddard, Henning and McPillan \cite{Goddard2014}, \NP-completeness was shown for various graph classes like general graphs, \emph{split}, \emph{planar}, \emph{chordal bipartite} and \emph{circle} graphs \cite{Henning2019, Kloks2021}.
Contrary, there exist polynomial-time algorithms for \emph{AT-free}, \emph{block} and \emph{interval} graphs as well as for \emph{graphs of bounded mim-width}, \emph{graphs of bounded clique-width} \cite{Kloks2021, Galby2020,Courcelle1990,Henning2022,Henning2019}.
After giving an update on the problem, we start a systematic look through the lens of \textit{parameterized complexity} by showing that \sdom is $\WTWOhs$-hard for bipartite graphs and split graphs when parameterized by solution size.
On the positive side, we extend a technique proposed by Alber et al. \cite{Alber2004} for \dom to construct a linear kernel of size $\kernelsize k$ for \sdom in planar graphs by giving suitable reduction rules.
 
 This result further complements known linear kernels for other domination problems like \cdom, \rbdom, \efdom, \eddom, \idom and \dirdom on planar graphs.

\textbf{Keywords: }Domination; Semitotal Domination; Parameterized Complexity; Planar Graphs; Linear Kernel 
} 
\end{abstract}

\chapter{Zusammenfassung}


Ein Graph \G und eine Menge $D$ wird als \textit{halbtotale stabile Menge} bezeichnet, falls $D$ eine stabile Menge und jeder Knoten $v \in D$ maximal einen Abstand von zwei zu einem anderen Zeugen $v' \in D$ besitzt. 

Das \msdom Problem frägt nach einer halbtotalen stabilen Menge von minimaler Kardinalität. 
Sei $\gamma_{t2}(G)$ die minimale Kardinalität einer halbtotalen stabilen Menge. Diese ist zwischen der minimalen stabilen Menge $\gamma(G)$ and der minimalen total stabilen Menge $\gamma_t(G)$ eingezwängt.
Gegeben \G und ein positives $k$, das \sdomdG s Problem frägt, ob $\gamma_{t2} \leq k $ ist.

Nachdem das Problem von Goddard, Henning und McPillan \cite{Goddard2014} eingeführt wurde, konnte \NP-vollständigkeit für viele Graphklassen wie \emph{allgemeine}, \emph{split}, \emph{plättbare}, \emph{chordal bipartite} und \emph{zirkuläre} Graphen bereits gezeigt werden \cite{Henning2019, Kloks2021}.
Andererseits, existieren polynomialzeit Algorithmen sowohl für \emph{AT-freie}, \emph{block} und \emph{interval} Graphen, als auch für \emph{Graphen mit beschränkter mim-width} und \emph{Graphen mit beschränkter clique-width} \cite{Kloks2021, Galby2020,Courcelle1990,Henning2022,Henning2019}.

Nach einer umfassenden Analyse zum Stand des Problems, beginnen wir eine systematische Analyse aus Sicht \textit{parametrisierter Komplexität} und zeigen, dass \sdom $\WTWOhs$-hart für bipartite und split Graphen ist, wenn parameterisiert durch die Größe der Lösungsmenge.
Basierend auf vorangegangener Arbeit \cite{Alber2004,Garnero2018} war es uns möglich Reduktionsregeln anzugeben, die einen linearen Problemkern der Größe $\kernelsize k$ für plättbare Graphen erzeugt.
 Dies vervollständigt existierende lineare Problemkerne ähnlicher Problem wie \cdom, \rbdom, \efdom, \eddom, \idom oder \dirdom.

{\sffamily

\textbf{Schlagworte}: Stabile Menge; Halbtotale Stabile Menge; Parametrisierte Komplexität; Plättbare Graphen; Linearer Problemkern 

}
\end{abstract}