\afterpage{%
\newgeometry{
top=1.25in,
bottom=1.25in,
left=1.25in,
right=1.25in,
bindingoffset=0.25in,
heightrounded
}
\addcontentsline{toc}{chapter}{Acknowledgments}
\thispagestyle{empty}

\vspace*{20mm}

\begin{center}
{\usekomafont{section} Acknowledgments}
\end{center}
\vspace{10mm}

% ACADEMIC
I have many people to thank for their support, but first and foremost, I would like to thank my supervisor \textit{Paloma}!
Without your valuable ideas, patience and feedback, I would not have been able to write this thesis and have stayed motivated for such a long time. 
Our weekly discussions were really helpful and I could not have wished for better guidance. 
Thank you for always having time for my questions and ideas and supporting me wherever I needed help. 
Apart from this, without your initial crusade against the university's bureaucracy and all the effort you put into your side project of ``Finding him a Ph.D.'', I might not have arrived so well in Copenhagen!

I would like to extend my gratitude to my professor at TUM, \textit{Debarghya}, for instantly agreeing to formally supervise my thesis. 
Your immediate willingness to take on this role and the uncomplicated and instant communication was highly appreciated!
%

Moreover, I would like to thank the whole \textit{Algorithms Group} at ITU for letting me be a part of the group.
From the moment I joined, you all made me feel welcome and integrated, and I am grateful for the opportunity to have written my thesis in such a friendly, helpful and productive environment.
Thank you, \textit{Thore}, for ``getting the initial ball rolling'' and enabling this stay.

Special thanks to \textit{Jan Arne} in Bergen for his introductory course into parameterized complexity. 
Without this course and your motivating feedback afterward, I might not have tried to write my thesis in this area.

%% NON-ACADEMIC
Thank you to my \textit{family} for always being there for me and supporting me, regardless of how far I am away.
Furthermore, I would like to acknowledge the assistance of my \textit{befriended ducks} and their quacky influence on some parts of the thesis.

Lastly, I would like to thank openAI's \textit{ChatGPT Dec 15} for supporting me in writing this acknowledgments section and \textit{Dall-E 2} for the immense amount of creativity that went into the chapter's illustrations!
What a time to be alive!

\cleardoublepage{}

\clearpage
\restoregeometry}